Network Data Collection for Artifical Intelligence

### 2020-02-27 paper2/paper2.tex
Update paper2.tex

Hypervisors like VirtualBox or VMware provide the possibility to set up full virtual computers on a physical host where Docker containers are encapsuled sandboxes on an existing operating system like illustrated in Fig.~\ref{docker-vm}. It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solutions which can be used in most of the cases also on our computers with some exceptions, we could use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms like AWS to support high-load scenarios e.g. big denial-of-service attacks. \cite{b8}

@@

Fig.~\ref{docker-vm} shows a possible simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor could be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.

@@

@@

>>>>

Hypervisors like VirtualBox or VMware provide the possibility to set up full virtual computers on a physical host (see Fig.~\ref{docker-vm}a) while Docker containers are encapsuled sandboxes on an existing operating system (see Fig.~\ref{docker-vm}b). It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solution which can be used in most of the cases also on our computers with some exceptions, we could use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms like AWS to support high-load scenarios e.g. big denial-of-service attacks. \cite{b8}

@@

Fig.~\ref{design-flow} shows a possible simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor could be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.

@@

Before the network traffic can be analysed, it has to be recorded first. Therefore, this chapter will give an overview of the available third-party software which can be used to record all the incoming network traffic. The functional requirements for a tool are chiefly the pace of handling the network traffic. All of these tools are client-based tools. Means that the software needs a client to be set up and used. This means that either the network target for the traffic has to be a client or the e.g. switch has to clone a port with all the incoming and outgoing traffic and direct all the data to a client running one or more of these tools. In some cases, analysing of network traffic can take much longer than the data is send or received by the network which means, that all the data need to be buffered or stored. In this case a packet-to-disk packet recorder is needed. This device can capture large amount of network traffic with a data rate of up to 40 Gbit/s and write it into files.

\subsection{pcap Library}

Every tools needs APIs\footnote{Application Programming Interface} to capture all the traffic sent through the network interface. Therefore, libraries were made for both Unix-like and Windows based operating systems. While \textit{libpcap} is used for Unix-like operating systems, a Windows system need the library called \textit{WinPcap}. With an pcap library software has the ability to tap all the network traffic from the selected interface. Based on the possibility to include the library in \textbf{C} and \textbf{C++}, \textit{pcap} can be used very easily into software. With the release of \textit{libpcap} 1.0.0, the zero-copy mechanism was implemented which allows the software to read the network traffic directly without copying the data from kernel space to user space.

\subsection{Network Recording Tools}

In this section we will itemise five well known and useful network recording tools. Some of the tools are console based tools, the other do have a GUI or both. All of these tools are client-based tools. Means that the software needs a Client to be set up and used. This means that either the network target for the traffic has to be a client or the e.g. switch has to clone a port with all the incoming and outgoing traffic and direct all the data to a client running one or more of these tools.

\subsection*{tcpdump}

Especially in the world of Unix based operating systems, \textit{tcpdump} is one of the best known tools for monitoring and sniffing network traffic. \textit{tcpdump} is exclusively command line based tool. This property makes \textit{tcpdump} a tool for advanced console line users only. But once you get familiar with the commands and options of \textit{tcpdump}, it will get a  a very efficient and powerful tool for many applications. \textit{tcpdump} uses the \textit{libpcap} network library of Unix based operating systems for capturing network traffic.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.4]{tcpdump.png}}
\caption{tcpdump Network Capture}
\label{tcpdump}
\end{figure}

With the wide set of options, \textit{tcpdump} is a pretty agile tool for dumping any analysing network traffic. A few of the options are listed below \cite{wikiUbuntu}.

\begin{itemize}
\item \textbf{-i eth0} the traffic from the interface \textit{eth0} is captured
\item \textbf{-w example.dump} all the output is written into a declared file
\item \textbf{-e} the ethernet header will recorded too
\item \textbf{-r example.dump} parsing the file \textit{example.dump} into tcpdump
\end{itemize}

For the Windows enthusiasts a Windows derivative of \textit{tcpdump} is available. It is called \textit{WinDump}. \textit{WinDump} uses so called WinPcap library for Windows operating systems.  Which has the same APIs as libpcap for Unix-like systems. This means, network traffic captured, e.g. on a Ubuntu system can be analysed on a Windows 10 Client afterwards.

\subsection*{Wireshark}

\textit{Wireshark} is for good reason the best known cross-platform networking tool available. In 2006 \textit{Wireshark} was started as a fork of the software called \textit{Ethereal} by the Wireshark-Community due to trademark issues \cite{asrodiapatel2012}.  The performance of this tool is powerful and the set of functions is neatly arranged. By using GTK toolkit, \textit{Wireshark} has implemented a GUI \footnote{Graphical User Interface}\cite{suribatra2012}. The GUI is separated typically into three segmentations, traffic overview, details of selected packet and the raw data of each packet.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.48]{wireshark.png}}
\caption{Wireshark Network Capture}
\label{wireshark}
\end{figure}

A good asset of \textit{Wireshark} is its available set of filters for capturing and displaying network data. With the help of plugins, \textit{Wireshark} can even handle with new or dedicated protocols. Another big asset of \textit{Wireshark} is its capibility of capturing raw USB traffic from an USB-Port. By highlighting the traffic with different colours as shown in Fig.~\ref{wireshark} it's easier to scan for required traffic.

\subsection*{Netsniff-ng}

\textit{Netsniff} is a another Unix based tool for network analysis. \textit{Netsniff} was the first tool which had the ability to analyse the whole traffic with a zero-copy procedure, means that \textit{Netsniff} uses the same data as the kernel do. Based on this functional principle, \textit{Netsniff} is one of the best performing tools for network sniffing. \textit{Netsniff} is like \textit{tcpdump} exclusively an console based software. The set of options contains 38 capabilities on the latest version of \textit{Netsniff}: 0.6.4 (effective 26.02.2020).

\subsection*{Capsa}

The fourth tool is called \textit{Capsa} from \textit{Colasoft} founded 2001 in United States. \textit{Capsa} is suitable for real-time network data capturing both LAN and Wireless Interfaces. A big advantage of \textit{Capsa} is the ability to evaluate the network traffic into graphical output like diagrams. This feature can help identifying perpetrator of inadvertent network traffic quickly by a human. The free version of \textit{Capsa} is heavily restricted regarding available functions.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.30]{capsa.png}}
\caption{Graphical Evaluation of Network Traffic with Capsa}
\label{capsa}
\end{figure}

\subsection*{EtherApe}

Yet another tool for network monitoring is called \textit{EtherApe}. \textit{EtherApe} is an Unix based software with a meaningful graphic interface and graphical data output of network traffic. With the help graphical illustration anomalies like a DDoS attack can be detected easily as shown in Fig.~\ref{etherape}. Every host is shown as a node in circle, every connection is shown as link between two nodes and every protocol has an own colour for the link. With higher network traffic between two hosts the link between nodes is shown larger.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.37]{etherape.png}}
\caption{Graphic Representation of Network Traffic}
\label{etherape}
\end{figure}

@@

\bibitem{wikiUbuntu} ubuntuusers.de
\bibitem{asrodiapatel2012} P. Asrodia, H. Patel (2012). Analysis  of  Various  Packet  Sniffing  Tools  for Network  Monitoring  and  Analysis.
\bibitem{suribatra2012} S. Suri, V. Batra, Comparative Study of Network Monitoring Tools.
